% Copyright 2023 The terCAD team. All rights reserved.
% Use of this content is governed by a CC BY-NC-ND 4.0 license that can be found in the LICENSE file.

\subsection{Supporting Accessibility}
\markboth{Optimizing}{Supporting Accessibility}

Before delving into Flutter's accessibility capabilities, it's valuable to comprehend the significance of accessibility. 
Accessibility involves the design and development of applications that are usable by all individuals, including those 
with disabilities such as visual, auditory, motor, or cognitive impairments. Providing equal access to information 
and services for all users is a matter of ethical and social responsibility. By ensuring that our app is 
accessible \issue{34}{}, we broaden its user base to include a more diverse audience. Lastly, accessibility often 
constitutes as a legal obligation in many regions.

The \q{Semantics} and \q{Tooltip} widgets serve as the initial building blocks for enhancing accessibility. They play a 
critical role in assisting screen readers by providing context to users with visual impairments. It can be implemented 
in a way of wrapping button by duplicating a written title to a label of it (some elements, as \q{FloatingActionButton} 
contains the label in a scope of properties):

\begin{lstlisting}
// ./lib/widgets/wrapper/elevate_button_widget.dart
class ElevatedButtonWidget extends StatelessWidget {
  Widget build(BuildContext context) {
    final colorScheme = context.colorScheme;
    return Semantics(
      label: text,
      child: SizedBox(
        width: double.infinity,
        child: ElevatedButton(
          style: ButtonStyle(
            shape: MaterialStateProperty.resolveWith((states) => 
                const ContinuousRectangleBorder()),
            // Respond to user actions, such as mouse hover
            backgroundColor: 
              MaterialStateProperty.resolveWith<Color>((states) {
                if (states.contains(MaterialState.hovered)) {
                  return hoveredColor ?? 
                      colorScheme.onSecondaryContainer;
                }
                return backgroundColor ?? colorScheme.secondary;
              },
            )),
          onPressed: onPressed,
          child: Text(
            text,
            style: TextStyle(
            color: textColor ?? colorScheme.inversePrimary,
            shadows: const [],
// ... closing brackets
\end{lstlisting}

\noindent Regardless of its role as a canvas for creating user interfaces, Flutter excels in ensuring the accessibility 
of widgets, allowing them to seamlessly interact with screen readers like TalkBack on Android and VoiceOver on iOS. In 
this context, the semantic tree in Flutter closely aligns with the widget tree. Flutter integrates with the 
accessibility APIs of the underlying platforms, which means it can effectively communicate with screen readers. 
Semantics actions act as intermediaries between the operating system's accessibility APIs and the semantics nodes. 
That enables various interactions, including tapping, long-pressing, scrolling, accessibility focus transitions, and a 
range of other actions, thereby ensuring an accessible user experience.

To validate that our application complies with semantic assertions and provides the expected accessibility, we may 
employ the \q{SemanticsOwner} for testing. That enables us to conduct programmatically-driven tests on 
the behavior of the application's semantics tree:

\begin{lstlisting}
testWidgets('Test semantics actions', (WidgetTester tester) async {
  await tester.pumpWidget(App());
  final semantics = tester.getSemantics(find.text('Home'));
  final owner = tester.binding.pipelineOwner.semanticsOwner;
  owner.performAction(semantics.id,
      SemanticsAction.didGainAccessibilityFocus);
  owner.performAction(semantics.id, SemanticsAction.tap);
});
testWidgets('Test alternative inputs', (WidgetTester tester) async {
  await tester.pumpWidget(App());
  await tester.sendKeyDownEvent(LogicalKeyboardKey.control);
  await tester.sendKeyEvent(LogicalKeyboardKey.keyN);
  await tester.sendKeyUpEvent(LogicalKeyboardKey.control);
  await tester.pumpAndSettle(const Duration(seconds: 1));
  expect(find.text('Create new Transaction'), findsOneWidget);
});
\end{lstlisting}

\noindent The accessibility isn't limited solely to the text interpretation, by extending experience to effectively 
manage the focus for users who navigate through the app using keyboards or voice commands. As a navigation can be 
enhanced with keyboard shortcuts provided through the use of the \q{Listener}-widget. This feature is particularly 
valuable for users who rely on keyboard navigation (either for accessibility, or from desktop usage perspective). This 
not only adheres to accessibility guidelines but also makes our application more inclusive and user-friendly:

\begin{lstlisting}
// ./lib/widgets/wrapper/input_controller_wrapper.dart
class InputControllerWrapper extends StatefulWidget {/* ... */}

class InputControllerWrapperState 
    extends State<InputControllerWrapper> {
  @override
  Widget build(BuildContext context) {
    // Obtain the current zoom value from 'AppZoom'-provider
    zoom = Provider.of<AppZoom>(context, listen: false);
    // Wrap the widget with listeners
    return Listener(
      onPointerSignal: _onPointerSignal, // Listen for mouse input
      child: RawKeyboardListener(
        focusNode: focus,
        onKey: _onKeyPressed, // Listen for keyboard input
        child: widget.child,
      ),
    );
// ... other stuff
\end{lstlisting}

\begin{table}[h!]
  \begin{tabular}{ |p{7.8cm}||l|  }
    \hline
    Description & Shortcut\\
    \hline
    Open / Close the Navigation Drawer &  \key{Shift} + \key{Enter} \\
    Navigate Up                        &  \key{up} \\
    Navigate Down                      &  \key{down} \\
    Open Selected                      &  \key{Enter} \\
    Zoom In                            &  \key{Ctrl} + \key{+} \\
    Zoom In (with mouse)               &  \key{Ctrl} + \key{scroll down} \\
    Zoom Out                           &  \key{Ctrl} + \key{-} \\
    Zoom Out (with mouse)              &  \key{Ctrl} + \key{scroll up} \\
    Reset Zoom                         &  \key{Ctrl} + \key{0} \\
    Add new Transaction                &  \key{Ctrl} + \key{N} \\
    \hline
  \end{tabular}
  \caption{Shortcuts in the application} \label{tb:shortcuts}
\end{table}
