% Copyright 2023 The terCAD team. All rights reserved.
% Use of this content is governed by a CC BY-NC-ND 4.0 license that can be found in the LICENSE file.

\subsection{Marketing}
\markboth{Productionizing}{Marketing}

Marketing is a critical aspect of any product's journey from development to success. While traditional advertising can 
be costly, leveraging online platforms can be a cost-effective way to build brand awareness. Platforms like Facebook, 
Instagram, Twitter, and LinkedIn provide ample opportunities to engage with the audience through content calendars, 
regular posts, and interactions with followers. However, social media isn't just for promotion; it's a means to 
create a community around our product. That's why understanding the audience is a valuable part of marketing strategy 
(customer segmentation marketing and targeting, \cite{Fras20}).

The first crucial step in this process is to establish precise objectives for the product launch. Aggregating timelines 
and milestones can be particularly advantageous in this context. These milestones effectively highlight the dynamic 
and evolving nature of our product.

Some falsely believe that merely making their product or service available is enough, and customers will automatically 
find and purchase from them without any personal interaction. It has misled many founders, especially those who have 
heard stories about successful companies like Dropbox or Twilio that appear to have no sales staff. 

The launch is merely the start, not the conclusion. And sales skills are not innate; they can be learned like any other 
skill \cite{Dixo11}. Sales is simply another challenge to overcome, much like the technical hurdles we've faced before. 
Just as we've tackled complex technical issues by learning and problem-solving, we can approach sales with the same 
determination and willingness to learn. Sustain engagement with the audience by implementing post-launch strategies, 
such as frequent updates, responsive customer support, and soliciting reviews and feedback. The marketing is an ongoing 
process, and post-launch activities are equally vital. With the appropriate strategy, we can pave the path for our 
product's success in the market.
