% Copyright 2023 The terCAD team. All rights reserved.
% Use of this content is governed by a CC BY-NC-ND 4.0 license that can be found in the LICENSE file.

\subsection{Visioneering}
\markboth{Productionizing}{Visioneering}

Crafting a compelling product vision, the keystone of a product or service, demands a range of skills and discipline.
But most of the time it's started from basic questions \cite{Barr13}:

\begin{itemize}
  \item What is our vision for the enterprise?
  \item What is our purpose?
  \item Does a market exist and can we access it?
  \item Will we face competition?
  \item Can we clearly define our product and/or service?
  \item Have we formulated a plan?
  \item Do we need to involve other people?
  \item Do we need physical premises?
  \item How will we finance your enterprise?
  \item What potential risks may our enterprise face?
  \item What are our longer-term intentions and personal objectives?
\end{itemize}

\noindent Right now we've created a tiny application not even for managing personal finances, but for tracking expenses; 
but what if I tell you that the vision is \textbf{"to become a financial institution known for its integrity and ethical 
practices"} by declaring a core values as \q{Trust} (a solid reputation for reliability, transparency, and 
trustworthiness), \q{Community-Centric} (a sense of community among users, encouraging financial literacy), 
\q{Accessibility} (aspires to be universally accessible and serve users around the world, regardless of their 
capabilities and abilities). This vision reflects our unwavering commitment to provide financial services that go 
beyond mere functionality. We are dedicated to making a meaningful and positive impact on the financial well-being of
individuals and communities, promoting trust, inclusivity, and financial empowerment on a global scale with a motto: 
\textbf{"Financial Awareness is a Necessity"}.

In order to become a trustworthy financial institution, we must align our financial strategy with our vision. This requires customizing our revenue, cost, and profit projections to match our specific goals and the current market conditions:

\begin{itemize}
  \item Revenue Projections: Begin with conservative estimates of user growth, recognizing that we are initially a small 
  application. Then, estimate the number of users who might opt for subscriptions.

  \item Cost Projections: Consider the ongoing costs of development and maintenance. As the user base grows, allocate 
  resources for customer support to address inquiries and resolve issues. Budget for marketing and promotional 
  activities to acquire new users and retain existing ones. Due to our commitment to integrity and ethical practices, 
  allocate funds for compliance and security measures to ensure regulatory compliance and maintain user trust.

  \item Profitability: Keep in mind that it may take time to become profitable, especially if we're transitioning from 
  an expense-tracking app to a financial institution.
\end{itemize}

\noindent In order to transform our ambitious vision into reality, we must establish a structured plan. One highly 
effective approach is to implement Objectives and Key Results (OKRs) alongside Key Performance Indicators (KPIs). OKRs 
are a goal-setting framework \cite{Doer18} that helps organizations set, track, and measure their objectives and 
results. OKRs provide clarity on what needs to be achieved and how success is defined. KPIs, on the other hand, are 
quantifiable metrics \cite{Marr12} that are valuable for monitoring and evaluating progress toward specific business 
goals. KPIs offer a clear understanding of performance and whether it aligns with the desired outcomes. Incorporating 
OKRs and KPIs into our strategy is crucial for tracking progress, making data-driven decisions, and ensuring that we 
stay on course toward our vision. This can be empowered by the "8-Step Process for Leading Change" strategy 
\cite{Kott12}:

\begin{itemize}
  \item Create A Sense of Urgency
  \item Build A Guiding Coalition
  \item Form A Strategic Vision
  \item Enlist A Volunteer Army
  \item Enable Action By Removing Barriers
  \item Generate Short-Term Wins
  \item Sustain Acceleration
  \item Institute Change
\end{itemize}

\noindent For instance, let's define the OKR for the first quarter of 2026: Objective "Establish a strong market 
presence", Key Result "Achieve one million downloads of the application", Key Result "Maintain an active user base of at 
least one thousand users", Key Result "Bring two new contributors on board".
