% Copyright 2023 The terCAD team. All rights reserved.
% Use of this content is governed by a CC BY-NC-ND 4.0 license that can be found in the LICENSE file.

\subsection{[TBD] Securing Information}
\markboth{Productionizing}{Securing Information}

[TBD]

\subsubsection{Storing API keys}
\markboth{Productionizing}{Storing API keys}

Every API requires passing a secret key with each request to validate the identity. These keys should remain 
confidential (as not be a part of the \q{git} history). Even detaching credentials into a separate \q{.env}-file  
susceptible to leaks. The most secure way is to store secrets as environment variables during the compilation 
(\q{build}) or evaluation (\q{run}):

\begin{lstlisting}[language=bash]
flutter build --dart-define==KEY=SECRET \
    --dart-define==KEY2=SECRET2 \
    --dart-define==KEY3=SECRET3
\end{lstlisting}

\noindent To get the API key from an environment:

\begin{lstlisting}
String? apiKey = String.fromEnvironment('KEY', defaultValue: null);
\end{lstlisting}


\subsubsection{Encrypting Storage}
\markboth{Productionizing}{Encrypting Storage}

Encryption is a critical process in the realm of cybersecurity, as it involves transforming a plain text into its 
encoded format, bolstering the confidentiality, integrity, and overall security of sensitive information. The process 
of "hiding" information can be one-way direction (by taking \q{hash}-key from a value, and using it for a comparison) 
or bidirectional (decrypt with a cryptographic key). For the last, there are two primary types of encryption: symmetric 
(AES, 3-DES, SNOW) and asymmetric (RSA, Elliptic curve cryptography) encryption, which is also referred to as public 
key encryption. Symmetric encryption relies on a single shared key, which all parties involved use for both encrypting 
and decrypting data. In contrast, asymmetric encryption, often referred to as public-key encryption, employs a pair of 
keys: one for encryption and another distinct key for decryption purposes.

To "disable" (at least make harder) capability to change financial transactions directly, it may be used a sum control 
\q{hash}-key \issue{58}{}:

\begin{lstlisting}
// ./lib/_classes/data/transaction_log.dart
import 'package:crypto/crypto.dart';

class TransactionLog {
  static String getHash(Map<String, dynamic> data) {
    return md5.convert(utf8.encode(data.toString())).toString();
  }

  static Future<bool> load() async {
    // ... other stuff
    await for (var line in lines) {
      var obj = json.decode(line);
      if (getHash(obj['data']) != obj['type']['hash']) {
        continue; // Corrupted data... skip
      }
\end{lstlisting}

\noindent Additionally, to protect user data we should apply mechanics of lines encryption:

\begin{lstlisting}
// ./lib/_classes/data/transaction_log.dart
import 'package:encrypt/encrypt.dart';

class TransactionLog {
  static Encrypter get salt =>
      Encrypter(AES(Key.fromUtf8('32symbols-salt-for-encryption...')));

  static IV get code => IV.fromLength(8);(*@ \stopnumber @*)

  (*@ \startnumber{49} @*)
  // to encrypt content
  content = salt.encrypt(content, iv: code).base64;
  // to decrypt content
  content = salt.decrypt64(content, iv: code);
\end{lstlisting}

\noindent As a note, the usage of any external library for encryption (and not only) might be relevant to additional 
risks, as a failed upgrade ("dependency shock" \cite{Inki23}) or a breakable change (in case of \q{encrypt}-package, a 
failed decryption after a migration from 5.0.1 to 5.0.2 -- 
\href{https://github.com/leocavalcante/encrypt/issues/314}{https://github.com/leocavalcante/encrypt/issues/314}).
So, it's better to be chosen a built-in functionality even with an additional complexity; in our case, through the 
\q{dart:crypto}-library, which includes hashing, symmetric and asymmetric encryption.
